---
title: "CourseProject_#1"
author: "Kim"
date: "2017.7.27"
output: html_document
---

This is for Coursera Course Project 1. 


## Before the Instructions 

1.First, load the data.

```{r}
data <- read.csv("activity.csv")
str(data)
```

2. Processing for 'date' 

```{r}
data$date <- as.Date(data$date, format = "%Y-%m-%d")
str(data)
```




And then follow the instructions. 

## What is mean total number of steps taken per day ? 

1. The total number of steps taken per day.
```{r}
sum <- with(data, tapply(steps,date,sum,na.rm=TRUE))
sum
``` 

2. Make a histogram of the total number of steps taken each day. 
3. Calculate and report the mean and median of the total number of steps taken per day 

```{r}
hist(sum)
abline(v = mean(sum), col = "red", lwd = 4)
abline(v = median(sum), col = "blue", lwd = 4)
``` 

```{r, echo = FALSE}
cat("Mean value: ", mean(sum))
```

```{r, echo= FALSE}
cat("Median value: ", median(sum))
```

On the figure above, there are two vertical lines which stand for mean and median.
Red line is for mean of sum, and blue line is for median of sum.DF




## What is the average daily activity pattern ? 
 
  1. Make a time series plot on every interval. 
  
```{r}
avg <- with(data,tapply(steps,interval,mean,na.rm=TRUE))
plot(row.names(avg),avg,type = 'l', lwd = 3)
```
  
  
  2. Which 5-minute interval on average across all the days in the dataset, 
      contains the maximum numbers of step?

```{r}
cat("Time interval which has the maximum numbers of step : ", row.names(avg)[which.max(avg)])
```



## Imputing missing values

# What is 'imputation' ? 

In statistics, imputation is the process of replacing missing data with      substituted values.  - Wikipedia 
 
 
  1. Calculate and report the total number of missing values in the dataset
  
```{r} 
cat("Total number of NAs: ", sum(sapply(data$steps, function(x) sum(length(which(is.na(x)))))))
``` 


  2. Devise a strategy for filling in all of the missing values in the dataset.
     (could use the mean / median for that day, or the mean for that 5-minute
     interval,etc.)
    
    -> I will impute the data with the mean for that 5-minute interval. 
    
    
  3. Create a new dataset that is equal to the original dataset but with the missing
     data filled in. 
    

```{r}

avg_by_interval <- with(data,tapply(steps,interval,mean,na.rm =TRUE))
num_of_rows <- dim(data)[1]  # the num of data. 
ch <- data[c(1,3)]
ch_date <- data[c(2)]
s <- sapply(ch$steps, function(x) length(which(is.na(x))))
names <- as.integer(names(avg_by_interval))

z <- as.data.frame(avg_by_interval)
z <- cbind(names,z) 

 # 's' stands for indicating which one is 'NAs' 
 # So , 's[i] == 1' means that we need to process on it. 

for(i in 1:num_of_rows){
   
  if(s[i] == 1)
  {
    ch[i,1] <- subset(z$avg_by_interval , z$names == ch[i,2])
  }
  
}


 # In 'ch' , steps & interval are configurated. 
 # Merging date and 'ch' 


mrg <- cbind(ch,ch_date)  # Mrg indicates the new dataset with the missing data 
                          # filled in. 


```

<br>

  4. Make a histogram based on the new dataset.(mrg) 
     What is the impact of imputing missing data on the estimates of the total 
     daily number of steps?

```{r}
# new dataset : mrg 
s <- with(mrg, tapply(steps,date,sum,na.rm=TRUE))
hist(s)
``` 

```{r} 
cat("Mean: ", mean(s))
``` 
```{r}
cat("Median: ", median(s))
```


 As shown above, histogram is different from first one. 
 By imputing the data, we could get more 'gaussian-likely' form.
 Because we got more data by substituting NAs with real values. 
 The more we get N, density will go to the normal based on statistical reason. 

 Also, by imputing, I could extract same values with mean and median. 

<br>

## Are there differences in activity patterns between weekdays and weekends? 

```{r}
mrg$days <- weekdays(mrg$date) # Adding new column indicating days. 
head(mrg)
```

Make 2 dataset. 
One for weekdays and the other for weekends. 

 1. Create a new factor variable in the dataset with two levels- 
    "weekday" and "weekend" indicating whether a given date is a weekday or weekend.
     <br>
     NOTICE: 
     MY R OUTPUT ENVIRONMENT IS BASED ON 'KOREAN'. 
     I COULDN'T CHANGE MY ENVIRIONMENT ALTHOUGH I TRIED SEVERAL TRIALS. 
      
     配夸老: Saturday 
     老夸老: Sunday 
     
     <br> 
     
```{r}

w <- factor()

for(i in 1:dim(mrg)[1]){

if(mrg[i,]$days =="配夸老" | mrg[i,]$days=="老夸老"){
  w <- rbind(w,"weekend")
}else{
  w <- rbind(w,"weekday") 
}
}

mrg <- cbind(mrg,w) # mrg contains 'weekdays' column ! 


``` 
 
  <br> 
 
  2. Make panel plot containing a time series plot of the 5-minute interval.
     I'll use 'aggregate' function. 

```{r}

# Using aggregate function 

avg_by_sw <- aggregate(steps ~ interval + w , data = mrg , mean) 
library(lattice)

xyplot(steps~ interval | w, data = avg_by_sw , type = 'l',  lwd = 2, layout = c(2,1), xlab = "Interval with every 5-minutes", ylab ="Mean of Steps", main =  "Steps ~ Interval", panel = function(x,y,...){
  
panel.abline(h = mean(y), col = "red", lwd = 3)
panel.xyplot(x,y,...)
  
})

```
 <br> 
 
  The red horizontal line indicates mean of each steps of given time interval. 
  In general,as shown above, people walk more on weekends. 
  








 
 
 
